import fs from 'fs';

const latexCode = `\\documentclass[11pt,a4paper]{article}

% ---------- Packages ----------
\\usepackage[top=1.2cm, bottom=1.2cm, left=1.2cm, right=1.2cm]{geometry}
\\usepackage{enumitem}
\\usepackage{titlesec}
\\usepackage{hyperref}
\\usepackage{xcolor}
\\usepackage{parskip}
\\usepackage{fontawesome5}
\\usepackage[many]{tcolorbox}

% ---------- ATS-Friendly Font ----------
\\usepackage{helvet}
\\renewcommand{\\familydefault}{\\sfdefault}

% ---------- Settings ----------
\\pagenumbering{gobble}
\\setlength{\\parindent}{0pt}
\\setlength{\\parskip}{3pt}
\\renewcommand{\\baselinestretch}{1.05}

\\setlist[itemize]{
    noitemsep,
    topsep=2pt,
    parsep=0pt,
    partopsep=0pt,
    leftmargin=*,
    label=\\textbullet
}

% ---------- Section Formatting ----------
\\titleformat{\\section}
  {\\large\\bfseries}{}{0em}{}
  [\\vspace{-4pt}\\titlerule]

\\titlespacing{\\section}{0pt}{10pt}{6pt}

% ---------- Document ----------
\\begin{document}

\\begin{tcolorbox}[colback=white, colframe=black, 
                  boxrule=0.8pt, arc=3pt,
                  left=10pt, right=10pt, top=8pt, bottom=8pt,
                  breakable]

% ---------- Header ----------
\\begin{center}
  {\\Large\\bfseries ABHIRAM BHUVANAGIRI} \\\\[4pt]
  {\\large\\bfseries Full Stack Developer} \\\\[8pt]

  \\faPhone\\ +91-9390545520 \\quad $|$ \\quad
  \\faEnvelope\\ \\href{mailto:abhiii.1818@gmail.com}{abhiii.1818@gmail.com} \\quad $|$ \\quad
  \\faLinkedin\\ \\href{https://www.linkedin.com/in/abhiram-bhuvanagiri-394a4a377}{LinkedIn} \\quad $|$ \\quad
  \\faGithub\\ \\href{https://github.com/Abhiram-Bhuvanagiri}{GitHub}
\\end{center}

% ---------- Profile ----------
\\section{Profile Summary}

Full Stack Developer skilled in React, Next.js, Node.js, Express.js, MongoDB, and Generative AI technologies. Experienced in building scalable web applications, integrating LLMs and APIs, and developing automation solutions. Strong problem-solving abilities with a solid foundation in Data Structures and Algorithms.
% ---------- Education ----------
\\section*{Education}
\\textbf{VITS Engineering College} \\hfill \\textit{Nov 2022 -- May 2026} \\\\
Computer Science and Engineering \\\\
Cumulative GPA: 7.0 / 10.0 \\\\
Relevant Coursework: Python, JavaScript, Tailwind CSS, Data Structures and Algorithms

% ---------- Experience ----------
\\section*{Experience}

\\textbf{Gen AI Engineer Intern} \\hfill \\textit{Nov 2025 -- Apr 2026} \\\\
\\textbf{SyncAI} \\hfill \\textit{Remote}

\\begin{itemize}
  \\item Built and deployed LLM-powered applications using LangChain and Hugging Face Transformers.
  \\item Implemented RAG pipelines with vector databases to improve contextual response accuracy.
  \\item Designed prompt engineering workflows for optimized AI-generated outputs.
  \\item Integrated AI functionalities into full-stack applications using FastAPI and React.
  \\item Improved inference efficiency and reduced latency through optimized API handling.
\\end{itemize}

% ---------- Projects ----------
\\section*{Projects}

\\textbf{\\href{https://stock-market-app-six.vercel.app/sign-in}{AI-Powered Real-Time Stock Market App}}
\\begin{itemize}
  \\item Built a real-time stock market web app using Next.js, Inngest, and MongoDB.
  \\item Integrated financial APIs for live data with automated background updates.
  \\item Implemented AI-driven insights for intelligent trading suggestions.
  \\item Enabled secure authentication and alerts using Better Auth and Node Mailer.
\\end{itemize}

\\textbf{\\href{https://ai-mock-interviews-opal-six.vercel.app/}{AI-Driven Voice Interview Simulation Platform}}
\\begin{itemize}
  \\item Developed a real-time AI interview platform using Next.js and Tailwind CSS.
  \\item Integrated Vapi for speech recognition and AI-based voice interaction.
  \\item Used Firebase for authentication and real-time data handling.
  \\item Simulated realistic interview scenarios with instant AI feedback.
\\end{itemize}

\\textbf{Automated Job Application Bot}
\\begin{itemize}
  \\item Built an automation bot using n8n for daily job tracking and filtering.
  \\item Integrated LinkedIn APIs with AI-based job relevance scoring.
  \\item Automated workflows to eliminate manual job searching.
  \\item Delivered real-time alerts via email and Slack notifications.
\\end{itemize}

% ---------- Skills ----------
\\section*{Skills}
\\textbf{Languages:} Python, JavaScript \\\\
\\textbf{Frontend:} React, Next.js, Tailwind CSS \\\\
\\textbf{Backend:} Node.js, Express.js, MongoDB, Supabase \\\\
\\textbf{Tools:} Git, GitHub, VS Code, Postman, Figma, n8n, LLMs

% ---------- Certifications ----------
\\section*{Certifications \\& Learning}
\\begin{itemize}
  \\item Full Stack Web Development — The Odin Project, freeCodeCamp
   \\item Generative AI with Large Language Models — DeepLearning.AI \\& AWS
\\end{itemize}

\\end{tcolorbox}

\\end{document}`;

fs.writeFileSync('resume.tex', latexCode);
